\large{\bf Looking forwards and backwards through locally regulated populations }

### 2022-04-10 forwards-and-backwards.tex
.
conceptual figure

\begin{figure}
    \begin{center}
        FIGURE
    \end{center}
    \caption{
        Conceptual figure of the model.
        Left: (cartoon) plot of $\gamma$, $r$, $\mu$, and $F$ against density,
        showing the equilibrium point.
        Right: cartoon of interaction and dispersal distances.
        \label{fig:model_setup}
    }
\end{figure}

@@

Although our proof of Theorem\ref{thm:lineages}

@@

    \theta \int (f(x) - f(y)) g(x) \widetilde q_\theta(y, dx)
    &\approx

@@

>>>>

\begin{figure}
    \begin{center}
        \includegraphics{figures/conceptual_figure}
    \end{center}
    \caption{
        Conceptual figure of the model.
        \textbf{(A)} Example plot of $\gamma$, $\mu$, and $F$
        (calculated with $r=1$) against scaled local population density.
        In this example, both birth and death rates increase with population density,
        but death increases faster,
        and equilibrium occurs where they cross
        (and hence where $F=0$).
        \textb{(B)} Cartoon of interaction ($\epsilon$) and dispersal ($\sigma$) distances.
        \label{fig:model_setup}
    }
\end{figure}

@@

Although our proof of Theorem~\ref{thm:lineages}

@@

    \theta \int (f(x) - f(y)) g(x) \widetilde q_\theta(y, dx) \\
    &\qquad \to

@@

    &\qquad =
